---
title: "Just a Test"
author: "Aaron Gullickson"
date: "3/3/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(knitr)
library(kableExtra)
library(texreg)
load("example_data/movies.RData")
```

## How much money does each genre make?

Here is a paragaph. Ipsem lopsum  Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum Ipsem lopsum 

Here is another paragraph.

Lets look at this first by a tapply command:

```{r boxoffice-by-genre}
sort(tapply(movies$BoxOffice, movies$Genre, mean)) %>%
  enframe("Genre", "Mean Box Office Returns") %>%
  kable(caption = "Mean box office returns by genre") %>%
  kable_classic()
```

Now lets do something different!

```{r boxoffice-genre-box, fig.cap="Distribution of box office returns by genre."}
ggplot(movies, aes(x=reorder(Genre, BoxOffice, median), y=BoxOffice))+
  geom_boxplot(fill="red")+
  labs(x=NULL, y="box office returns in millions USD")+
  theme_bw()+
  coord_flip()
```

The graph shows that *animation* movies make the most money and *romance* and *drama* make the least. Also, movies that make more in total have much larger variance typically.

```{r models, results='asis'}

model1 <- lm(BoxOffice~I(Runtime-90), data=movies)
model2 <- update(model1, .~.+I(Year-2001))
model3 <- update(model2, .~.+TomatoMeter)

knitreg(list(model1, model2, model3),
        caption="Linear models predicting box office returns",
        caption.above=TRUE,
        digits=3,
        custom.coef.names=c("Intercept","Runtime (in minutes)",
                            "Year of release","Tomato meter"))
```



