---
title: "Nonlinearity Assignment for Soc 413/513"
author: "Your Name Here"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      error = FALSE)
# load required libraries
source("check_packages.R")
```

```{r load-data, include=FALSE}
# load the analytical datam named `worldbank`
load(here("output","worldbank.RData"))
```

In this report, you should explore the relationship between GDP per capita and CO2 emissions per capita in a country using 2018 data from the World Bank. The analytical dataset is named `worldbank` and has only these two variables. You should focus on the following issues:

* Addressing non-linearity in the relationship between these two variables. 
* Addressing iid violations such as heteroskedasticity (watch for cone shapes!).

In your analysis, you should treat GDP per capita as the independent variable (i.e. the variable on the x-axis). Your analysis should include:

* Graphical exploration of the relationship, and text description of what this graphical exploration reveals.
* A final model which bests fit the underlying functional form and a description of what that model tells you about the relationship.

You should create new code chunks as need to do your analysis. Use one code chunk per figure. 

```{r}
ggplot(worldbank, aes(x=gdpcap, y=co2cap))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()
```


```{r}
ggplot(worldbank, aes(x=gdpcap, y=co2cap))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_smooth(method="lm", se=FALSE, color="red")+
  scale_x_log10()+
  theme_bw()
```

```{r}
model1 <- lm(co2cap~log(gdpcap), data=worldbank)
augment(model1) %>%
  ggplot(aes(x=.fitted, y=.std.resid))+
  geom_point()+
  geom_hline(yintercept=0, linetype=2)+
  theme_bw()
```

```{r}
model2 <- lm(log(co2cap)~log(gdpcap), data=worldbank)
augment(model2) %>%
  ggplot(aes(x=.fitted, y=.std.resid))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_hline(yintercept=0, linetype=2)+
  theme_bw()
```

```{r}
ggplot(worldbank, aes(x=gdpcap, y=co2cap))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_smooth(method="lm", se=FALSE, color="red")+
  scale_x_log10()+
  scale_y_log10()+
  theme_bw()
```

```{r}
model3 <- lm(log(co2cap)~log(gdpcap)+I(log(gdpcap)^2), data=worldbank)
augment(model3) %>%
  ggplot(aes(x=.fitted, y=.std.resid))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_hline(yintercept=0, linetype=2)+
  theme_bw()
```

```{r}
ggplot(worldbank, aes(x=gdpcap, y=co2cap))+
  geom_point()+
  geom_smooth(se=FALSE)+
  geom_smooth(method="lm", formula = y~x+I(x^2), se=FALSE, color="red")+
  scale_x_log10()+
  scale_y_log10()+
  theme_bw()
```
